Modeling dependencies in multivariate seabird distributions: linking spatial dependence graph models to centrality measures

### 2017-02-08 paper1_jrss.tex
updaten refs and fixed def error

\documentclass{statsoc}
\usepackage[]{graphicx}
\usepackage[]{color}

@@

%============================================
\begin{abstract}
  Graphical modeling of seabird distributions.
\end{abstract}

@@

\begin{itemize}
\item We estimate the conditional spatial dependence structure between different seabird species
\item edges express the partial (pairwise) interrelation between two species conditional on al remaining species
\item we omit to implement a formal test statistic as we assume that dependence might vary between species
\item we set a threshold indicating weak/ intermediate partial effects
\item we combine spatial dependence graph model with importance tools of social network analysis
\item info can provide important insides for species conservation
\item eg which are the most important species in the overall graph
\end{itemize}

@@

@@

%============================================
\section{Results}
============================================

@@

\end{document}

>>>>

\documentclass{statsoc}
\usepackage[]{graphicx}
\usepackage[]{color}
\let\proof\relax 
\let\endproof\relax

@@

%============================================
\begin{abstract}
  Graphical modeling of seabird distributions. Simultaneous estimation of conditional spatial interrelation for a subset of $79$ seabird species by means of a spatial dependence graph model (SDGM). Linkage to Social network analysis toolbox to detect the most influential species (in term of importance within the estimated SDGM)  
\end{abstract}

@@

\begin{itemize}
\item We estimate the conditional spatial dependence structure between different seabird species
\item that is, structural dependence between two patterns conditional on all remaining patterns
\item so not interrelation between points $i$ and $j$, but interrelations between components $i$ and $j$ where $i$ and $j$ are sets of points within a bounded planar region.
\item edges express the partial (pairwise) interrelation between two species conditional on al remaining species
\item we omit to implement a formal test statistic as we assume that dependence might vary between species
\item we set a threshold indicating weak/ intermediate partial effects
\item we combine spatial dependence graph model with importance tools of social network analysis
\item info can provide important insides for species conservation
\item eg which are the most important species in the overall graph
\end{itemize}

@@

Primary idea by \cite{Eckardt2016}, extension to multivariate spp with quantitative marks by \cite{Eckardt2016b}

Analysis was carried out using the \texttt{sdgm} R package of \cite{Eckardt2016a}.

@@

%============================================
\section{Results}
%============================================

@@

\bibliographystyle{rss}
\bibliography{lit}
\end{document}
